Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
modified:   softxmt-hotpar2011.tex

 Techniques from graph analytics have found important applications in
  areas such as social networks and bioinformatics. These irregular
  problems present a challenge for parallel machines: obtaining
  performance is not straightforward. Multithreading works well for
  such problems, but large-scale implementations of the technique like
  the Cray XMT are expensive, non-commodity machines.

@@

Figure~\ref{fig:system-overview} shows the structure of our
proposal. It is composed of multiple nodes built with commodity
processors, communicating over an Infiniband network. We add two
components: a runtime system, responsible for executing the user's
threads, and a global memory manager, responsible for facilitating
memory requests to the non-coherent global memory shared across the
nodes.  This memory manager is the only component that might require
hardware, but we are exploring a mix of hardware and software
implementations.

@@

The value of the information in extremely large and sparse graphs is
rapidly growing.  The GraphCT toolkit \cite{ediger-graphct} used an XMT to perform
sophisticated analysis on data from Twitter, identifying important
actors and their networks of influence, and it can scale to the full
size of graphs such as Facebook's friend network.
\section{Programming model}
\label{sec:model}

Our shared-memory programming model partitions the overall address
space into a global shared address space and per node private address
spaces.  Locality may be exploited directly by the programmer in the
node private address spaces, just as in a conventional cache-coherent
multiprocessor node.  In contrast, locality cannot be exploited in 
the global space.

\todo{explain why global address space is good}

@@

There are three main concerns in designing the coroutine
mechanism. First, the working set of each coroutine must be small, so
many coroutines can be active without monopolizing the cache. Second,
context switches must be fast, so that overhead does not swamp actual
work. Third, when a coroutine yields, we must choose a suitable
coroutine to run next.

@@

>>>>

 Techniques from graph analytics have found important applications in
  areas such as social networks and bioinformatics. These irregular
  problems present a challenge for parallel machines: obtaining
  performance is not straightforward. Multithreading works well for
  such problems, but the only large-scale implementation of the technique
  is the Cray XMT, an expensive, non-commodity machine.

@@

Figure~\ref{fig:system-overview} shows the structure of our
proposal. It is composed of multiple nodes built with commodity
processors, communicating over an Infiniband network. We add two
components: a runtime system, responsible for executing the user's
threads, and a global memory manager, responsible for facilitating
memory requests to the non-coherent global memory shared across the
nodes.  We are exploring a mix of hardware and software
implementations of the memory manager.

@@

\section{Programming model}
\label{sec:model}

Our shared-memory programming model partitions the overall address
space into a global shared address space and per node private address
spaces.  Locality may be exploited directly by the programmer in the
node private address spaces, just as in a conventional cache-coherent
multiprocessor node.  In contrast, locality cannot be exploited in the
global space: its value is in providing high bandwidth random access
to any word in a shared data structure by any processor.

@@

There are three main concerns in designing the coroutine
mechanism. First, the working set of each coroutine must be small, so
many coroutines can be active without trashing the cache. Second,
context switches must be fast, so that overhead does not swamp actual
work. Third, when a coroutine yields, we must choose a suitable
coroutine to run next.

@@

The value of the information in extremely large and sparse graphs is
rapidly growing.  The GraphCT toolkit \cite{ediger-graphct} used an XMT to perform
sophisticated analysis on data from Twitter, identifying important
actors and their networks of influence, and it can scale to the full
size of graphs such as Facebook's friend network.
